3. Analysis Plan

### 2021-07-02 analysis/reports/rmd/02_dataProcessing.Rmd
udate reports

```{r readData}
# read replication data
DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
               stringsAsFactors = FALSE) %>%
  data.table()
```

>>>>

```{r readData}
# read replication data
DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
               stringsAsFactors = FALSE) %>%
  data.table()

# subset complete cases
DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
```

### 2021-07-02 analysis/reports/rmd/03_dataAnalyses.Rmd
udate reports

The rank sum test yields a p-Value of `r rs1` for the mean ```stock``` a.k.a _Wealth_ during the last period of the game.

@@

@@

@@

@@

The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.

@@

          column.labels   = c("Wealth", "Gini"),
          dep.var.labels.include = FALSE,
          column.separate = c(2, 2),
          model.numbers = FALSE,
          header=FALSE,
          covariate.labels = c("female", "age", "risk",
                               "quick thinker",
                               "easily offended",
                               "very satisfied",
                               "very dependent",
                               "generally happy",
                               "work important",
                               "family important",
                               "friends important",
                               "religion important",
                               "politics important",
                               "most people trusted",
                               "hard work better",
                               "government responsible",
                               "incomes equal"),
          notes = "Robust standard errors in parentheses, clustered by group ID.",

>>>>

The table above displays summary statistics for the 10th period's ```stock``` a.k.a _Wealth_. The rank sum test yields a p-Value of `r rs1` for the mean wealth during the last period of the game.

The following table shows a simple regression to illustrate differences in the 10th period's wealth between the replication's data and GMTV's data.

@@

These information are also plotted over all periods in the following figure.

@@

The following figure plots the Gini-coefficient These over all periods.

@@

The following table shows a simple regression to illustrate differences in the 10th period's Gini coefficient between the replication's data and GMTV's data.

@@

The table above displays summary statistics for the 10th period's ```gini``` .
The rank sum test yields a p-Value of `r rs2` for the mean ```gini``` during the last period of the game.

@@

          column.labels   = c("Wealth", "Gini"),
          dep.var.labels.include = FALSE,
          column.separate = c(2, 2),
          model.numbers = FALSE,
          header=FALSE,
          covariate.labels = c("female", "age", 
                               # "risk",
                               "quick thinker",
                               "easily offended",
                               "very satisfied",
                               "very dependent",
                               "generally happy",
                               "work important",
                               "family important",
                               "friends important",
                               "religion important",
                               "politics important",
                               "most people trusted",
                               "hard work better",
                               "government responsible",
                               "incomes equal"),
          notes = "Robust standard errors in parentheses, clustered by group ID.",
